How to Write Theses\\ With Two Line Titles

### 2020-04-15 chapters/methodology/collection.tex
New

\section{Tools}
\subsection{Jupyter}
The Jupyter Notebook is an open-source web application that supports data cleaning and transformation, numerical simulation, statistical modeling, data visualization, machine learning, etc. by allowing us to create and share documents that contain live code, equations, visualizations and narrative text. Jupyter allows for displaying the result of computation inline in the form of rich media (SVG, LaTeX, etc.). The Jupyter notebook combines two components:
\begin{itemize}
  \item \textbf{A web application}: a browser-based tool for interactive authoring of documents which combine explanatory text, mathematics, computations and their rich media output.
  \item \textbf{Notebook documents}: a representation of all content visible in the web application, including inputs and outputs of the computations, explanatory text, mathematics, images, and rich media representations of objects.
\end{itemize}
Jupyter notebook is gaining rapid popularity in the field of data science for making sharing documentation and codes for replication very easy. In this project, the codes are written in python notebook which can be accessed from http://github.com/.

\subsection{Tensorflow}
TensorFlow\textsuperscript{TM} is an open source software library developed within Google’s AI organization by the Google Brain team with a strong support for machine learning and deep learning. Its flexible architecture allows easy deployment of computation across a variety of platforms (CPUs, GPUs, TPUs), and from desktops to clusters of servers to mobile and edge devices. It is being used at a number of well known companies like Uber, Google, AMD, etc. for high performance numerical computation and machine learning. While TensorFlow is capable of handling a wide range of tasks, it is mainly designed for deep neural network models. It will serve as baseline to test the metamorphic relations identified in section \ref{MRused}.

\section{Algorithm}
\subsection{Convolutional neural network}
\subsection{2-layer neural network}

\section{Dataset}
\subsection{MNIST Dataset}
The MNIST database of handwritten digits maintained by Yann LeCun \cite{MNIST}, has a training set of 55,000 examples, and a test set of 10,000 examples. It is a subset of a larger set available from NIST. The digits have been size-normalized and centered in a fixed-size image. It is a good database for people who want to try learning techniques and pattern recognition methods on real-world data while spending minimal efforts on preprocessing and formatting. The MNIST database was constructed from NIST's Special Database 3 and Special Database 1 which contain binary images of handwritten digits. The original black and white (bilevel) images from NIST were size normalized to fit in a 20x20 pixel box while preserving their aspect ratio. The images were centered in a 28x28 image by computing the center of mass of the pixels, and translating the image so as to position this point at the center of the 28x28 field.

@@

\subsection{Format of Dataset}
The data is stored in a very simple file format designed for storing vectors and multidimensional matrices. All the integers in the files are stored in the MSB first (high endian) format used by most non-Intel processors. There are 4 files:
\begin{itemize}
  \item train-images-idx3-ubyte: training set images
  \item train-labels-idx1-ubyte: training set labels
  \item t10k-images-idx3-ubyte:  test set images
  \item t10k-labels-idx1-ubyte:  test set labels
\end{itemize}
The format of training and test files are described in the following table.
\begin{table}[ht]
\centering
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{offset} & \textbf{type}    &      \textbf{value}    &      \textbf{description} \\
\hline
0000  &   32 bit integer & 0x00000801(2049) & magic number (MSB first) \\
\hline
0004  &   32 bit integer & 60000       &     number of items \\
\hline
0008  &   unsigned byte  & ??          &     label \\
\hline
0009  &   unsigned byte  & ??          &     label \\
\hline
\multicolumn{4}{|c|}{\textbf{........}} \\
\hline
xxxx  &   unsigned byte  & ??          &     label \\
\hline
\multicolumn{4}{|c|}{\textbf{The label values are 0 to 9.}} \\
\hline
\end{tabular}
\caption{Training data file format.}
\label{tbl:training-file-format}
\end{table}

>>>>

In this chapter, we will discuss the tools we used to perform our experiment. 
We used Python as the programming language to implement our code. We chose Python because of its popularity and easy syntax. There are also plenty of Python libraries like Tensorflow, Keras, and scikit-learn available to easily implement machine learning, deep-learning, natural language processing algorithms. Along with Python as the programming language, we also used the following programs, tools, and datasets to perform our experiment.
 \section{Tools}
\subsection{HCC}
Due to the high computation requirements for some dataset we needed a faster and reliable hardware. The Holland Computing Center (HCC) claim to be the fastest resource in the state of Nebraska. HCC provides these services to researcher and students associated with any campus of the University of Nebraska system. Some shared services are available for free and dedicated services can be obtained for a modest price. We used their servers to run our Jupyter notebooks.

\subsection{Jupyter Notebook}
Jupyter notebook is part of project Jupyter, which aims at providing an interactive interface for development across multiple platforms and programming languages. Jupyter's web interface supports data cleaning, data transformation, and visualization, numerical operations, etc. It allows us to create live code snippets and equations and shows results of inline computation right next to the code in the form of rich media (SVG, LaTeX, etc.). It combines two components: 
\begin{itemize}
  \item \textbf{A web application}: a web-based interactive tool to write code, markdown, etc. It also displays the rich media output.
  \item \textbf{Notebook documents}: a representation of all the content written and displayed using the web application.
\end{itemize}
Jupyter notebook is gaining rapid popularity in the field of data science for making sharing documentation and codes for replication very easy. In this project, we wrote the codes in python notebook, which can be accessed from our GitHub repository.

\subsection{Tensorflow}
% TensorFlow is an end-to-end open source platform for machine learning. It has a comprehensive, flexible ecosystem of tools, libraries and community resources that lets researchers push the state-of-the-art in ML and developers easily build and deploy ML powered applications
TensorFlow\textsuperscript{TM} is an open-source software library developed within Google’s AI organization by the Google Brain team with strong support for machine learning and deep learning. Its flexible architecture allows easy deployment of computation across a variety of platforms (CPUs, GPUs, TPUs), and from desktops to clusters of servers to mobile and edge devices. Several well-known companies like Uber, Google, AMD, etc. use Tensorflow for high-performance numerical computation and machine learning tasks. While TensorFlow is capable of handling a wide range of tasks, it is designed mainly for deep neural network models. Tensorflow provides API for loading, manipulating, and using the MNIST dataset identified in section \ref{dataset}. We also used TensorFlow to implement neural network and convolutional neural network defined insection \ref{Algorithms}

% TensorFlow\textsuperscript{TM} is an open source software library developed within Google's AI organization by the Google Brain team with a strong support for machine learning and deep learning. Its flexible architecture allows easy deployment of computation across a variety of platforms (CPUs, GPUs, TPUs), and from desktops to clusters of servers to mobile and edge devices. It is being used at a number of well known companies like Uber, Google, AMD, etc. for high performance numerical computation and machine learning. While TensorFlow is capable of handling a wide range of tasks, it is mainly designed for deep neural network models. It will serve as baseline to test the metamorphic relations identified in section \ref{MRused}. Tensorflow provides api for loading the MNIST dataset identified in section \ref{dataset}. We also used tensorflow to implement neural network and convolutional neural network defined in section \ref{Algorithms}

\subsection{Scikit-learn}
Scikit-learn is a Python module for machine learning built on top of SciPy and is distributed under the 3-Clause BSD license.
It provides APIs to a range of supervised and unsupervised learning algorithms via a consistent interface in Python.

\section{Algorithms}\label{Algorithms}
In order to answer research questions two and three, we implemented some popular machine learning algorithms to provide quantitative data on the effect of metamorphic relations on the accuracy of datasets and their classes. We used TensorFlow and scikit-learn to implement the following machine learning algorithms.

\subsection{Convolutional neural network}
The images in the MNIST dataset is a one-dimensional vector of 784 features (28x28 pixels). We first reshape the images to match the picture format height x width x channel. Each image in the MNIST dataset is now a single-channel of 28x28x1 size. The images are then fed into the network as input. The first convolution layer has 32 filters with a kernel size of five. The activation function we used is the ReLU function, and the output from this layer is fed into a pooling layer. The data goes through another iteration of convolution and pooling before being flattened and sent to the fully connected layer. The output layer gives us a number that corresponds to the class of the image it is assigned.

\subsection{Neural network}

 Hidden fully connected layer with 256 neurons. Each hidden layer is made up of a set of neurons, where each neuron is fully connected to all neurons in the previous layer, and where neurons in a single layer function completely independently and do not share any connections. If the image is a 64 by 64 greyscale image, then we'd have 64x64=4,096 input neurons, with the intensities scaled appropriately between 0 and 1. The output layer will contain just a single neuron, with output values of less than 0.5 indicating "input image is not a 9", and values greater than 0.5 indicating "input image is a 9 ". The input pixels are greyscale, with a value of 0.0 representing white, a value of 1.0 representing black, and in between values representing gradually darkening shades of grey. The second layer of the network is a hidden layer.

\subsection{Naive Bayes}
We used scikit-learn to implement the Naive Bayes algorithm. We transformed the images into a one-dimensional vector of 784 features. 
Using the $sklearn.naive\_bayes.MultinomialNB()$ function we created a Naive Bayes classifier, which is then fitted using the $fit()$ function, which takes the images and labels as input and fits the classifier according to the images and labels. The resulting classifier is then used to predict the labels of test data.

\subsection{$k$-Nearest Neighbor}
 We used scikit-learn to implement our $k$-nearest neighbor algorithm. Scikit's $sklearn.neighbors$ module provides the functionality to implement unsupervised and supervised neighbors-based learning methods. 
 The KNeighborsClassifier function from the $sklearn.neighbors$ module implements learning based on the $k$ nearest neighbors of each query point, where $k$ is an integer value specified by the user. The k-neighbors classification in KNeighborsClassifier is the most commonly used technique. Since the optimal value $k$ is dependent on data, we ran the experiment with multiple values of $k$ and found that the $k$=3 produces the best accuracy. In general, a larger $k$ suppresses the effects of noise but makes the classification boundaries less distinct.
 We used Euclidean distance as the distance metric and assigned equal weights to all the query points. In some cases, it might be better to assign weights based on the distance. The close query point contributes more to the fit, and the ones far contribute less. For our case, the uniform weight with a simple majority vote of the nearest neighbors worked just fine.

\subsection{SVM}
We also implemented the support vector machine algorithm using scikit-learn. The $sklearn.svm.SVC$ class is based on libsvm and is capable of performing multi-class classification. Internally, they use libsvm and liblinear to handle all computations. These libraries are wrapped using C and Cython. It supports multi-class classification on a one-vs-one scheme. In this scheme, a classifier is created for each pair of classes and during prediction, the class which receives most votes is assigned to the data point. In the event of a tie, we selected the class with the highest total confidence calculated by summing over the pair-wise classification confidence. 
As the other classifiers, $skleran.SVM$ also takes as input two arrays: an array of training samples and another array of class labels. The training samples and labels are passed to $fit$ function, which fits the SVM model according to the data. The resulting model is then used to predict the labels of test data.

\section{Datasets}\label{dataset}
In order to create metamorphic properties that can be used by multiple image datasets and are not data-dependent, we tested our metamorphic properties on three different datasets. We choose the following three datasets, but the experiment can be easily replicated on other datasets.

\subsection{MNIST Dataset}
The MNIST database of handwritten digits maintained by Yann LeCun \cite{MNIST} has a training set of 55,000 examples and a test set of 10,000 examples. It is a subset of a larger set available from NIST. The digits have been size-normalized and centered in a fixed-size image. It is an excellent database for people who want to try learning techniques and pattern recognition methods on real-world data while spending minimal efforts on preprocessing and formatting. The MNIST database was constructed from NIST's Special Database 3 and Special Database 1, which contain binary images of handwritten digits. The original black and white (bi-level) images from NIST were size normalized to fit in a 20x20 pixel box while preserving their aspect ratio. The images were centered in a 28x28 image by computing the center of mass of the pixels, and translating the image so as to position this point at the center of the 28x28 field.

@@

\subsection{Format of Dataset}
The data is stored in a very simple file format designed for storing vectors and multidimensional matrices. All the integers in the files are stored in the MSB first (high endian) format used by most non-Intel processors. There are four files:
\begin{itemize}
  \item train-images-idx3-ubyte: training set images
  \item train-labels-idx1-ubyte: training set labels
  \item t10k-images-idx3-ubyte:  test set images
  \item t10k-labels-idx1-ubyte:  test set labels
\end{itemize}
The format of training and test files are described in the following table.
\begin{table}[ht]
\centering
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{offset} & \textbf{type}    &      \textbf{value}    &      \textbf{description} \\
\hline
0000  &   32 bit integer & 0x00000801(2049) & magic number (MSB first) \\
\hline
0004  &   32 bit integer & 60000       &     number of items \\
\hline
0008  &   unsigned byte  & ??          &     label \\
\hline
0009  &   unsigned byte  & ??          &     label \\
\hline
\multicolumn{4}{|c|}{\textbf{........}} \\
\hline
xxxx  &   unsigned byte  & ??          &     label \\
\hline
\multicolumn{4}{|c|}{\textbf{The label values are 0 to 9.}} \\
\hline
\end{tabular}
\caption{Training data file format.}
\label{tbl:training-file-format}
\end{table}

### 2020-04-15 chapters/methodology/properties.tex
New

\section{Identifying Metamorphic Relations} 
We identified seven metamorphic properties for each dataset used: rotation, shearing, shading, shifting along x-axis, shifting along-axis, zooming along x-axis, zooming along y-axis. Each image in the testing dataset (digit, letter, and, fashion) was transformed using the seven metamorphic properties. We used Keras image preprocessing functions to apply these transformations to the test data in each dataset to generate new data to measure robustness.
\subsection{Rotate}
The test images from each dataset is transformed The rotation transformation algorithm takes in an image and an angle in degrees as parameter and rotates the image with the given angle. For each angle in [\ang{-50}, \ang{50}] we transformed each image Each image (digit, letter, and, fashion) is rotated clockwise and counter clockwise between angles [\ang{-50}, \ang{50}]. 
    \begin{figure}[!htbp]
        \centering
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/rotate1.png}
            \caption{Angle: \ang{-50}}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\textwidth]{images/rotate2.png}
            \caption{Angle: \ang{0}}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/rotate3.png}
            \caption{Angle: \ang{50}}
            \label{fig:Rotate-misclass0}
        \end{subfigure}
        \caption{Rotation property applied to Digit 3.}
        \label{fig:Rotate-misclassifications}
    \end{figure}
    \FloatBarrier

\subsection{Shear}  
    \begin{figure}[!htbp]
        \centering
        \begin{subfigure}[b]{.3\textwidth}
            \includegraphics[width=\linewidth]{images/shear1.png}
            \caption{Angle: \ang{-50}}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \includegraphics[width=\textwidth]{images/shear2.png}
            \caption{Angle: \ang{-50}}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \includegraphics[width=\linewidth]{images/shear3.png}
            \caption{Angle: \ang{-50}}
            \label{fig:Rotate-misclass0}
        \end{subfigure}

        \caption{Shear property applied to Digit 4.}
        \label{fig:Rotate-misclassifications}
    \end{figure}
    \FloatBarrier

\subsection{Shading}
    \begin{figure}[htb!]
        \centering
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/shade1.png}
            \caption{Value: 0}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\textwidth]{images/shade2.png}
            \caption{Value: 80}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/shade3.png}
            \caption{Value: 99}
            \label{fig:Rotate-misclass0}
        \end{subfigure}

        \caption{Shade property applied to Digit 9.}
        \label{fig:Rotate-misclassifications}
    \end{figure}
    \FloatBarrier

\subsection{Shifting in the X direction}
    For any value above x the image was completely out of the frame.
    \begin{figure}[htb!]
        \centering
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/shiftx1.png}
            \caption{Value: -10}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\textwidth]{images/shiftx2.png}
            \caption{Value: 0}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/shiftx3.png}
            \caption{Value: 10}
            \label{fig:Rotate-misclass0}
        \end{subfigure}

        \caption{Shift X property applied to Digit 7.}
        \label{fig:Rotate-misclassifications}
    \end{figure}
    \FloatBarrier

\subsection{Shifting in the Y direction}
    \begin{figure}[htb!]
        \centering
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/shifty1.png}
            \caption{Value: -10}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\textwidth]{images/shifty2.png}
            \caption{Value: 0}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/shifty3.png}
            \caption{Value: 10}
            \label{fig:Rotate-misclass0}
        \end{subfigure}

        \caption{Shift Y property applied to Digit 5.}
        \label{fig:Rotate-misclassifications}
    \end{figure}
    \FloatBarrier

>>>>

\section{Identifying Metamorphic Relations} \label{identifyingMR}
To answer our first research question, we implemented some affine transformations on the datasets as possible candidates for metamorphic properties. We observed that applying these affine transformations on the dataset to a very small degree produced similar accuracy as that of the original dataset. Thus we selected these five transformations as metamorphic properties for each dataset: rotate, shear, shade, shift the image along $x$-axis, and shift the image along $y$-axis. Each image in the testing dataset (MNIST, Fashion-MNIST, and EMNIST-Letter) was transformed using these five metamorphic properties. We used Keras image preprocessing functions to apply these transformations to the test data in each dataset to generate new data to measure robustness.

There are $10000$ test images in the MNIST dataset. There are $10$ class labels from $0$ to $9$, and each class label has $1000$ samples. We applied the following metamorphic properties to each test image.
\subsection{Rotate}
% Since we are dealing with image datasets, we hypothesize that small changes to the images by rotating them clock-wise or counter clock wise would not have drastic effect on the accuracy of model. To test our hypothesis we rotated the test data at each angle between [\ang{-50}, \ang{50}]. 
The first metamorphic property we identified was rotating the images on the $z$ axis. To implement the rotate property, we used the Keras ImageDataGenerator class. ImageDataGenerator implements $apply\_transform()$ method, which can be used to rotate images by passing the argument $'theta'$ along with the angle to rotate the image. Every image in the three datasets was rotated for every angle in [$-50$, $50$]. This generated 100 versions of the follow-up test dataset of the original data, where each version differs from the last by $1$ degree of rotation. We expect that certain digits with symmetry (like $0$) will not be affected that much by the rotate property. 
% The test images from each dataset is transformed For each angle in [\ang{-50}, \ang{50}] we transformed each image Each image (digit, letter, and, fashion) is rotated clockwise and counter clockwise between angles [\ang{-50}, \ang{50}].  The rotation transformation algorithm takes in an image and an angle in degrees as parameter and rotates the image with the given angle. 
    \begin{figure}[!htbp]
        \centering
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/rotate1.png}
            \caption{Angle: \ang{-50}}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\textwidth]{images/rotate2.png}
            \caption{Angle: \ang{0}}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/rotate3.png}
            \caption{Angle: \ang{50}}
            \label{fig:Rotate-misclass0}
        \end{subfigure}
        \caption{Rotate property applied to Digit 3.}
        \label{fig:Rotate-property}
    \end{figure}
    \FloatBarrier

\subsection{Shade}
We represent the pixels of the MNIST images as floating point numbers between 0 and 1 where 0 is white, and 1 represents black. To apply the shade transformation, we increased the non-black pixels by $0.01$ for every image until they became black.
    \begin{figure}[htb!]
        \centering
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/shade1.png}
            \caption{Value: 0}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\textwidth]{images/shade2.png}
            \caption{Value: 80}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/shade3.png}
            \caption{Value: 99}
            \label{fig:Rotate-misclass0}
        \end{subfigure}

        \caption{Shade property applied to Digit 9.}
        \label{fig:Shade-property}
    \end{figure}
    \FloatBarrier

\subsection{Shear} 
To shear the images, we used the image pre-processing library offered by Keras. The ImageDataGenerator class generates batches of tensor image data with real-time data augmentation. We used the ImageDataGenerator's $apply\_transform()$ method to apply a transformation to an image according to given parameters. The $apply\_transform()$ method takes in the image, transformation type, and, the amount of transformation to be applied as a parameter. It then applies the transformation and returns a transformed version of the input in the same shape.
The transformation parameter we used here was $shear$, and the images were transformed for every angle in $[-50, 50]$.

    \begin{figure}[!htbp]
        \centering
        \begin{subfigure}[b]{.3\textwidth}
            \includegraphics[width=\linewidth]{images/shear1.png}
            \caption{Angle: \ang{-50}}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \includegraphics[width=\textwidth]{images/shear2.png}
            \caption{Angle: \ang{-50}}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \includegraphics[width=\linewidth]{images/shear3.png}
            \caption{Angle: \ang{-50}}
            \label{fig:Rotate-misclass0}
        \end{subfigure}

        \caption{Shear property applied to Digit 4.}
        \label{fig:Shear-property}
    \end{figure}
    \FloatBarrier

\subsection{Shift the image along the X axis(ShiftX)}
Since the images are $28$ pixels wide, shifting the images by more than 28 pixels in either direction moved the images out of the frame completely. Thus, we transformed the test datasets by moving each image by pixels between 0 and 28 in both the X directions. We used ImageDataGenerator's $apply\_transform()$ function with $tx$ parameter and a pixel value in order to perform this transformation. This generated 56 follow-up test dataset of the original data where each version differs from the last by $1$ pixel shift along the $x$ axis.
    \begin{figure}[htb!]
        \centering
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/shiftx1.png}
            \caption{Value: 10}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\textwidth]{images/shiftx2.png}
            \caption{Value: 0}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/shiftx3.png}
            \caption{Value: -10}
            \label{fig:Rotate-misclass0}
        \end{subfigure}

        \caption{ShiftX property applied to Digit 7.}
        \label{fig:ShiftX-property}
    \end{figure}
    \FloatBarrier

\subsection{Shift the image along the Y axis(ShiftY)}
The last metamorphic property we identified was shifting the images on the Y-axis. We used ImageDataGenerator's $apply\_transform()$ function with $ty$ parameter to transform the test data. Since the images are 28x28 pixels, we shifted the images by each pixel between 0 and 28 pixels in both Y directions. 
    \begin{figure}[htb!]
        \centering
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/shifty1.png}
            \caption{Value: -10}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\textwidth]{images/shifty2.png}
            \caption{Value: 0}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/shifty3.png}
            \caption{Value: 10}
            \label{fig:Rotate-misclass0}
        \end{subfigure}

        \caption{ShiftY property applied to Digit 5.}
        \label{fig:ShiftY-property}
    \end{figure}
    \FloatBarrier

The follow-up test images have the same structure and labels as the original image. After generating all the transformed versions of the datasets, they were saved to be used as follow-up test cases for our machine-learning algorithms. The section \ref{identifyingMR} also answers our first research question.

After generating the follow-up test cases and implementing the machine-learning algorithms, we tested the trained model on the five follow-up test cases. The rotate, shade, and shear properties have 100 versions of the transformed original dataset each. The shiftX and shiftY properties have 56 versions of original test data as follow-up test data. Each of the 412 follow-up test datasets was then tested on the trained models, and their accuracy was calculated. We will discuss our findings in the next section.

### 2020-04-15 chapters/results/figures.tex
New

\subsection{Overall Accuracy or true positive}\label{4.1.1}
In this section we tested the algorithms using the transformed test dataset. The test datatsets were applied with increasing value of transformations identified in \ref{identifyingMR}. A copy of these new datasets generated from the original dataset by applying the transformations were saved to serve as follow-up test cases. For example, the MNIST dataset was transformed by applying the shading metamorphic relation for every pixel between [-28,28]. The models were then tested with transformed test data and their accuracy were calculated for every follow-up test data. The following graphs shows the change in accuracy of the whole dataset as the degree of transformation is changed. The X-axis shows the value of metamorphic transformation applied to the original test data and the Y-axis shows the accuracy corresponding to that value of transformation.
    \begin{figure}[htb!]
    \centering
    \begin{subfigure}[b]{0.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{chapters/results/MT/Rotate.png}
        \caption{Rotation}
    \end{subfigure}
    \begin{subfigure}[b]{ 0.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{chapters/results/MT/Shade.png}
        \caption{Shading}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{chapters/results/MT/Shear.png}
        \caption{Shearing}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{chapters/results/MT/ShiftX.png}
        \caption{Shifting along X-axis}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{chapters/results/MT/ShiftY.png}
        \caption{Shifting along Y-axis}
    \end{subfigure}
    \caption{Accuracy of the algorithms.}
    \label{fig:Accuracy}
    \end{figure}

 From the graphs in \ref{fig:Accuracy} we can see that different algorithms respond differently to the follow-up datasets. To quantify this difference, we calculated the area under curve for all the curves in \ref{fig:Accuracy}. The following table shows the area under each curve in \ref{fig:Accuracy}.
    \begin{table}[ht]
    \centering
        \begin{tabular}{|c|c|c|c|c|c|}
        \hline
         & CNN & NN & NB & KNN & SVM \\
         \hline
        Rotation & 91.01 & 81.70 & 70.31 & 72.71 & 66.60  \\
        \hline
        Shading & 64.40 & 75.51 & 79.52 & 50.26 & 52.23 \\
        \hline
        Shearing & 94.07 & 87.95 & 74.23 & 84.26 & 81.08 \\
        \hline
        Shift-X & 48.51 & 32.06 & 27.36 & 42.33 & 36.88 \\
        \hline
        Shift-Y & 30.32 & 26.19 & 26.55 & 34.04 & 29.90 \\
        \hline
        \end{tabular}
        \caption{Area under curve.}
        \label{tbl:test-file-format}
    \end{table}
    Figure 4.1(a) through (c) shows the variation in accuracy of . A higher area under curve means 
    KNN has a higher accuracy but, the area under curve is much lower than the convolutional neural network and the 2-layer neural network. Suggests that if you want to use metamorphic transformation to reveal flaw in an algorithm some transformations may be preferable over others.

>>>>

\subsection{Overall Accuracy or true positive}\label{4.1.1}
In this section, we compare the accuracy of the original MNIST test data to the accuracy of the follow-up test cases. After generating the model and testing the original test data, we used the same model to test the follow-up transformed test dataset. The test datasets were applied to the models with the increasing value of transformations. 
As we discussed in section \ref{identifyingMR}, the follow-up test cases were generated by transforming the original dataset with an increasing value of metamorphic properties.  A copy of these new datasets was saved to serve as follow-up test cases. The follow-up test images have the same structure and labels as the original image. For example, the MNIST dataset was transformed by applying the shiftX metamorphic property for every pixel between [-28,28]. The models were then tested with transformed test data, and their accuracy was calculated for every follow-up test data. The following graphs show the change in accuracy of the whole dataset with the change in the degree of transformation. The X-axis shows the value of metamorphic transformation applied to the original test data, and the Y-axis shows the corresponding accuracy to that value of transformation.
    \begin{figure}[htb!]
    \centering
    \begin{subfigure}[b]{0.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{chapters/results/MT/Rotate.png}
        \caption{Rotation}
    \end{subfigure}
    \begin{subfigure}[b]{ 0.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{chapters/results/MT/Shade.png}
        \caption{Shading}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{chapters/results/MT/Shear.png}
        \caption{Shearing}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{chapters/results/MT/ShiftX.png}
        \caption{Shifting image along X-axis}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\textwidth}
        \centering
         \includegraphics[width=\textwidth]{chapters/results/MT/ShiftY.png}
        \caption{Shifting image along Y-axis}
    \end{subfigure}
    \caption{Accuracy of the algorithms.}
    \label{fig:Accuracy}
    \end{figure}

 From the graphs in \ref{fig:Accuracy}, we can see that different algorithm respond differently to the follow-up datasets. To quantify this difference, we calculated the area under the curve for all the graphs in \ref{fig:Accuracy}. The following table shows the area under each curve in \ref{fig:Accuracy}.\\
    \begin{table}[H]
    \centering
        \begin{tabular}{|c|c|c|c|c|c|}
        \hline
         & CNN & NN & NB & KNN & SVM \\
         \hline
        Rotate & 91.01 & 81.70 & 70.31 & 72.71 & 66.60  \\
        \hline
        Shade & 64.40 & 75.51 & 79.52 & 50.26 & 52.23 \\
        \hline
        Shear & 94.07 & 87.95 & 74.23 & 84.26 & 81.08 \\
        \hline
        ShiftX & 48.51 & 32.06 & 27.36 & 42.33 & 36.88 \\
        \hline
        ShiftY & 30.32 & 26.19 & 26.55 & 34.04 & 29.90 \\
        \hline
        \end{tabular}
        \caption{Area under curve.}
        \label{tbl:rot-file-format}
    \end{table}

    In table \ref{tbl:rot-file-format}, the convolutional neural network has the highest area under the curve for the rotate, shear, and shiftX property. This means that, on average, the accuracy of the convolutional neural network does not decrease as much as the other algorithms when tested with the various degree of transformed follow-up test cases.
    On the other hand, KNN has the lowest area under the curve for the shade metamorphic property. Thus, the accuracy of the KNN program drops rapidly as the value of shade property in the test dataset increases.
    % Figure 4.1(a) through (c) shows the variation in accuracy of . A higher area under curve means 
    % KNN has a higher accuracy but, the area under curve is much lower than the convolutional neural network and the 2-layer neural network. Suggests that if you want to use metamorphic transformation to reveal flaw in an algorithm some transformations may be preferable over others.
